Community-conditioned language models for linguistic variation

### 2021-10-14 paper/paper1.tex
typo

For this purpose, we introduce (\cref{sec:cclm}) various 
Community-Conditioned Language Models (CCLMs for short),
which learnan embedding of the communites they are conditioned on 
as a side effect of their language modeling objective.
We test which architectures best make use of the community information and 
how and in what ways the resulting embeddings are
correlated with a social network-based representation of communities(\cref{sec:embedding-analysis}).
% , and model the degree to which a
% given message $m$ is acceptable in a given community $c$, by estimating the probability
% \(P(m \mid c)\).

>>>>

For this purpose, we introduce (\cref{sec:cclm}) various 
Community-Conditioned Language Models (CCLMs for short),
which learn embedding of the communites they are conditioned on 
as a side effect of their language modeling objective.
We test which architectures best make use of the community information and 
how and in what ways the resulting embeddings are
correlated with a social network-based representation of communities(\cref{sec:embedding-analysis}).
% , and model the degree to which a
% given message $m$ is acceptable in a given community $c$, by estimating the probability
% \(P(m \mid c)\).
